%\documentclass[letter]{report}
\documentclass[12pt,leqno]{ksudiss}
% \usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amsmath,amssymb,amsfonts,latexsym,cancel}
\usepackage[applemac]{inputenc}
\usepackage[english]{babel}
\usepackage{subfig}
\usepackage{makeidx}
\usepackage{float}
\usepackage{threeparttable}
\usepackage{xspace}
\usepackage{tabularx}
\usepackage[toc,page]{appendix}
\usepackage{subfiles}
\usepackage[version=4]{mhchem}
\usepackage{bm}
%\usepackage{xcolor}
%=============
%---jjp: class file didn't get even margins. I commented it out of class and include here.
\usepackage[letterpaper,
            % bindingoffset=0.2in,%
            left=1in,right=1in,top=1in,bottom=1in,%
            footskip=.25in]{geometry}
%---jjp: double spacing better this way too
\usepackage{setspace}
\doublespacing
%\usepackage[document]{ragged2e}
%=============
%
%------------------if using bibtex
\usepackage[backend=bibtex,style=phys]{biblatex}
%\bibliographystyle{newnsf}
\bibliography{jportman_talant}
%--------------------------------
%------------------if using biber
%\usepackage[backend=biber,style=numeric-comp,sorting=none,natbib=true]{biblatex}
%\usepackage[backend=biber,style=authoryear-icomp,sortlocale=de_DE,
%natbib=true,url=false,doi=true,eprint=false]{biblatex}
% \addbibresource{jportman_talant.bib}
%--------------------------------
\makeatletter
\def\blx@maxline{77}
\makeatother
% - Center pagenumber
\usepackage{fancyhdr}
%
\usepackage{csquotes}
%
\usepackage{chngcntr}

\counterwithin{figure}{section}
\counterwithin{table}{section}
\graphicspath{{figures/chap1_figs/}{figures/chap2_figs/}{figures/chap3_figs/}{figures/chap4_figs}{figures/chap5_figs}}

% =========
\usepackage[compact,sf,bf]{titlesec}
\titleformat{\chapter}[display]%
      {\center\Large\bfseries\sffamily}% formatting commands to apply to the whole heading
      {\chaptertitlename  \thechapter}% the label and number
      {10pt}% space between label/number and subsection title
      {}% formatting commands applied just to subsection title
      []% punctuation or other commands following subsection title

\titleformat{\section}%
      {\large\bfseries\sffamily}% formatting commands to apply to the whole heading
      {\thesection}% the label and number
      {10pt}% space between label/number and subsection title
      {}% formatting commands applied just to subsection title
      []% punctuation or other commands following subsection title
      % \titleformat{\subsection}{\normalsize\bfseries\sffamily}{$\square$~\thesubsection}{0em}{}[]
      \titleformat{\subsection}{\normalsize\bfseries\sffamily}{\thesubsection}{1em}{}
      \titleformat{\subsubsection}[runin]{\bfseries\sffamily}{\thesubsubsection}{1em}{}[.~]
%
\titlespacing{\subsubsection}{0ex}{1 .ex plus .1ex minus .2ex}{1pc}
\titlespacing{\subsection}{0ex}{2.ex plus .1ex minus .2ex}{-.5pc}
\titlespacing{\section}{0ex}{2.ex plus .1ex minus .2ex}{1ex}
\titlelabel{\thetitle.\quad}
% ========


\title{\large\bf The role of chain flexibility and conformational  \protect\\
  \large\bf  dynamics on Intrinsically Disordered Protein \protect\\
  \large\bf association}

\author{Talant Ruzmetov}
\namedegreedate{Ruzmetov, Talant  Ph.D., }
\pages{161}
\advisor{Dr. John J. Portman}
\degrees{B.Sc., National University of Uzbekistan, 2007 \\ 
         M.Sc., Mississippi State University, 2012 \\
         Ph.D., Kent State University, 2019}

\newcommand{\cdate}{August, 2019}

\makeindex

%----------------------------------------------------------------------
%todos
\usepackage[colorinlistoftodos,color=green!20,textsize=tiny]{todonotes}
\usepackage[normalem]{ulem} % use normalem to protect \emph for highlighting and short note
\newcommand\hl{\bgroup\markoverwith{\textcolor{yellow!20}{\rule[-.5ex]{2pt}{2.5ex}}}\ULon}
\newcommand\ghl{\bgroup\markoverwith{\textcolor{green!10}{\rule[-.5ex]{2pt}{2.5ex}}}\ULon}
\newcommand\bhl{\bgroup\markoverwith{\textcolor{blue!10}{\rule[-.5ex]{2pt}{2.5ex}}}\ULon}
\newcommand\rhl{\bgroup\markoverwith{\textcolor{red!10}{\rule[-.5ex]{2pt}{2.5ex}}}\ULon}
\newcommand{\todohl}[2]{\todo[color=yellow!20]{#1}\hl{#2}~}
\newcommand{\newtxt}[1]{\todo[color=blue!10]{new}\bhl{#1}~}
\newcommand{\rewrite}[1]{\todo[color=red!10]{rewrite}\rhl{#1}~}
\newcommand{\needref}[1]{\todo[color=orange!20]{ref: #1}~}
\newcommand{\todoin}[1]{\todo[inline]{\small #1}}
\newcommand{\todoitem}[1]{\todo[inline,caption={}]{\small #1}}
% ----------------------------------------------------------------------


\begin{document}
\frontmatter
\prefacesection{Acknowledgments}
\noindent

I am immensely grateful to have my family members for being supportive of my education
and motivating me throughout my undergraduate and graduate career. I feel blessed and
thankful to my mother Miyassar Atamuratova and father Adilbek Ruzmetov for the love,
care, nurture and continuous motivation they have been providing me with. IÕm very thankful
to have such an amazing life partner, my beloved wife Feruza Ruzmetova for being supportive
of my carreer and providing endless care and love for me and my kids. I am also grateful to
my other family members and friends, who have supported me along the way.

I would like to express infinite gratitude to my research advisor, Dr. John J. Portman for
providing his heartfelt support and guidance at all times and has given me inspiration and
suggestions in my quest for research in biophysics. Due to his endless efforts, I was able to
transition from amateur physicist to an expert computational and theoretical biophysicist.
In addition to introducing me to this amazing research field, Dr. Portman has given me
a step by step guidance on critical thinking process, scientific writing, programming, and
other tools crucial for my research that goes beyond the problem setup. While working under
his supervision, I also enjoyed the freedom to pursue the research and studies of my choice.
Without his able guidance and help, this thesis would not have been possible and I shall
eternally be grateful to him for his supervision.

My special gratitude goes to Constance Reho, Kelly Conley and other office staff in
the physics department. I would like to mention Academic Laboratory Manager, Mr. Greg
Putman and Dr. Mina Katramatou for providing a great many years of teaching experience.
I am also thankful to Dr. L\"ussem Bj\"orn for his demonstration
of efficient teaching methods, leadership, and management during my teaching assistantship in
an active learning course. I would like to express appreciation to my colleagues, Daniel Gavazzi
and alumnus Prithviraj Nandigrami for fun times we shared together (racquetball and card games),
technical support and insightful suggestions.

I would like to acknowledge financial support from the National Science Foundation for
part of the research presented in this dissertation.

I'm thankful to Ohio Supercomputer Center for computational resources made available.

Finally, despite all the assistance provided by Dr. Portman
and others, I take responsibility for the content of the material in this dissertation.


\startthesis
% - Center pagenumber
\pagestyle{fancy}
\renewcommand\headrulewidth{0pt}
\lhead{}\chead{}\rhead{}
\cfoot{\vspace*{1.5\baselineskip}\thepage}
%\tableofcontents
%
\chapter{\textbf{Introduction}}
\subfile{chapter1/chapter1.tex}
%
\chapter{\textbf{Coarse Grained Structure Based Model Simulations}}
\subfile{chapter2/chapter2.tex}
%
%
\chapter{\textbf{Role of flexibility in binding kinetics and affinity of pKID-KIX}}
\subfile{chapter3/chapter3.tex}
%
\chapter{\textbf{The Influence of Reconfiguration Dynamics on IDP Binding Kinetics}}
\subfile{chapter4/chapter4.tex}
%

\chapter{\textbf{Outlook}}

% \subfile{conclusion/conclusion.tex}

\subfile{outlook/outlook.tex}
%

%Appendices
%\begin{appendices}
%  \appendix
%  \chapter{\bf{Supplement for Chapter 4}} %\label{}
%  \subfile{appendix/chapter4.tex}
%  \chapter{\bf{Supplement for Chapter 5}} %\label{}
%  \subfile{appendix/chapter5.tex}
%\end{appendices}
\printbibliography
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
